%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modified Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (07/04/2020)
% 
% Author
% Nolan Mayersky(https://apurvmishra.xyz)
% Repository
% https://github.com/apurvmishra99/Modified-Deedy-Resume
% Original author of Deedy Resume:
% Debarghya Das (http://debarghyadas.com)
% His repository:
% https://github.com/deedydas/Deedy-Resume
%
%

%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{eurosym}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Nolan}{Mayersky}{ \urlstyle{same}\href{https://nolanm.dev/}{\bf nolanm.dev} |
\href{mailto:admin@nolanm.dev}{\bf admin@nolanm.dev} | \bf +12197770475 | \urlstyle{same}\href{https://github.com/nolyoi}{\bf Github} |
\urlstyle{same}\href{https://twitter.com/nolyoi}{\bf Twitter} |
\urlstyle{same}\href{https://linkedin.com/in/nolan-mayersky}{\bf Linkedin}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Flatiron School}
\descript{Software Engineering}
\location{\textbf{2020} | New York, New York}
\textbf{Classification: First Class} (Predicted)
\sectionsep

\subsection{Purdue University Northwest}
\descript{B.S. Computer Science}
\location{\textbf{2010} - \textbf{2012} | Hammond, Indiana}
\textbf{Classification: First Class} (Predicted)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Save Your Ocean}
\descript{| Co-founder \& Software Engineer }
\location{Dec \textbf{2019 } – Present | Ho Chi Minh City, Vietnam}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item As co-founder, I worked on shaping the product ideas, technologies used and business plans.
\item Developed RESTful APIs in Ruby and Padrino for the MVP.
\item Lead development of the user web application for the MVP in ReactJS.
\item The website and the company has now been launched and funded.
\end{tightemize}
\sectionsep

\runsubsection{University of Edinburgh}
\descript{| Teaching Support }
\location{Sep \textbf{2019 } – Present | Edinburgh, UK}
\begin{tightemize}
\item Teach Introduction to Haskell, Intro to Linux, Cognitive Science, Computation and Logic and general programming concepts to a cohort of over 400 students.
\item Marked and assisted in conduction of the exam. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{EasyShop}
\descript{| NodeJS, Python, APIs, Azure Cloud}
\location{Nov \textbf{2018 }}
\begin{tightemize}
\item EasyShop is a chabot to find products using pictures and get best possible deals.
\item Researched and found multiple third party APIs to accomplish our objectives and integrated it into our application by building a pipeline to move information efficiently.
\item The payment processing was done with the integration with Visa API .
\item The whole end to end solution is deployed on the Azure cloud and can be accessed on any social messaging service. 
\end{tightemize}
\sectionsep

\runsubsection{LinguaStream}
\descript{| Python, Tkinter, APIs, Google Cloud}
\location{Apr \textbf{2019 }}
\begin{tightemize}
\item LinguaStream is a real time translation and transcription service along with an analysis and reference platform.
\item Speech to Text transcription and translation are done through Google Cloud APIs.
\item Captioning service is written in Python using tkinter, APIs are made using the FastAPI library.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage}%
\hfill
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{\textbf{Confident:}}
Ruby \textbullet{} Python \textbullet{} JavaScript \textbullet{} \LaTeX\ \\ 
Rust \textbullet{} ReactJS \textbullet{} PostgreSQL \\
\location{\textbf{Familiar:}}
Flutter \textbullet{}
VueJS \textbullet{ }Rails \textbullet{} Shell
\sectionsep
\subsection{VCS \& Build Tools}
Git \textbullet{} TravisCI \textbullet{}Jenkins 
\sectionsep
\subsection{Cloud Services}
\location{\textbf{Familiar:}}
AWS \textbullet{} GCP \textbullet{} Azure
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards} 

\textbf{2019 } DigiEduHack \\
\textbf{2019 } HackKosice \\
\textbf{2019 } Cyber Defence Exercise\\
\textbf{2018 } Local Hack Day\\
\textbf{2018 } Oxford Hack \\
\textbf{2018 } Glasgow Hack \\
\textbf{2017 } DPS Noida

\section{Travel \& Conference Grants}

\textbf{\$250 } ELC, Edinburgh \\
\textbf{\$250 } PenApps, Philadelphia \\
\textbf{\textsterling 150 } Algothon, London \\
\textbf{\texteuro 150 } CEE Hacks, Prague\\
\textbf{\texteuro 150 } DENEFF EE Hack, Berlin\\
\textbf{\texteuro 120 } HackUPC, Barcelona\\
\textbf{\textsterling 75  } Hack Cambridge \\
\textbf{\texteuro 75    } Junction, Helsinki

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Algorithms and Data Structures \\
Data Analysis \\
Machine Learning \\
Software Testing \\
Functional Programming \\
OOP Programming \\
Software Engineering \\
Numerical Computation \\
Linear Algebra

\section{Activities}
EU Programming Society \\
EU Trading and Investment Club \\
CompSoc \\

\end{minipage}%
\end{document}  
\documentclass[]{article}
